Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-28 figures/diagram.tex
diagram: added delay lines
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@767 ccdd05d5-56c1-461a-bf98-85f6876523b4

\documentclass{amsart}
\usepackage{tikz}
\usepackage{signalflowdiagram}
\usetikzlibrary{external,fit,calc,chains,scopes}
\tikzexternalize
\begin{document}

@@

		\node[junction] at ($0.5*(u0) + 0.5*(u2) - (0.5, 0)$) (in\x tee) {};
		\node[resample, left=1.5cm of in\x tee] (in\x) {\tiny$\downarrow$};

@@

	\draw (in0) -- (in0tee) node[midway,above] {\small 4096 Hz};
	\draw (in1) -- (in1tee) node[midway,above] {\small 512 Hz};
	\draw (in2) -- (in2tee) node[midway,above] {\small 32 Hz};

>>>>

\documentclass{amsart}
\usepackage{tikz}
\usepackage{signalflowdiagram}
\usetikzlibrary{external,fit,calc,chains,scopes}
\tikzexternalize[force remake=true]
\begin{document}

@@

		\node[junction] at ($0.5*(u0) + 0.5*(u2) - (0.5, 0)$) (in\x tee) {};
		\node[resample, left=1.75cm of in\x tee] (in\x) {\tiny$\downarrow$};

@@

	\draw (in0) -- (in0tee) node[midway,above] {\small 4096 Hz};
	\draw (in1) -- (in1tee) node[midway,draw,fill=white,label=above:{\small delay}, label=below:{\small 512 Hz}] {$z^{-t_1 f_1}$};
	\draw (in2) -- (in2tee) node[midway,draw,fill=white,label=above:{\small delay},label=below:{\small 32 Hz}] {$z^{-\cdots}$};
